\documentclass[a4paper,twoside,titlepage]{book}
%begin preamble - main document spec info goes here
\usepackage{mathptmx}
\usepackage{makeidx}
%\usepackage{glossaries}
%\usepackage[toc]{glossaries}
\makeindex
%\makeglossaries
\title{The New Tetris: The First Ten Years 
\\(2004-2014)}
\author{Tom Hummel\thanks{J.D. Tawney}}
\date{\today}
\setcounter{tocdepth}{0}
%end preamble
\begin{document}
  \maketitle
  \tableofcontents
  \newpage
    \chapter{Preface}The following document is an exhaustive attempt at documenting all facets of The New Tetris. We attempt to cover our history with the game as well as pertenent resources from around the web. Additionally, essays on strategy and ideology referring to TNT explicitly and implicitly follow the history section. Following those, the real meat of this document is our records section - covering the entire official history of our TNT action dating back to 2004.
  \part{Official Format and Rules}
    \chapter{Basics of Play}
      \section{Cube Formations}Forming 4x4 cubes is the most significant method for scoring massive line scores. 
      \section{Cube Bonus Line Values}
      \index{cube}
    \chapter{Historical Changes}
      \section{Lines per Minute/Second}
    \chapter{Current Format and Rules}
  \part{An Oral History of The New Tetris}
    \chapter{Background and The Genesis}
    \chapter{Early Competition}
    \chapter{Spreadsheet Stats}
      \section{Letter Grades}
    \chapter{Website Stats}
  \part{Strategy Articles}
    \chapter{Speed of Play}
      \section{Fast from the start}
      \section{Slow from the start}
    \chapter{Directing Garbage}
      \section{Attacking the Strong}
      \section{Attacking the Weak}
    \chapter{Self Preservation at Any Cost?}
      \section{Seppuku}
      \section{Box or Nothing}
  \part{Philosphical Articles}
    \chapter{Essentials of Competition}
    \chapter{Data Granularity and Capture}
    \chapter{Measures of Greatness: Wins vs. Ratio}
    \chapter{Imperfection of the ``Power'' Metric}
  \part{Records and Stats}
    \chapter{Universe Totals}
    \chapter{Career Records}
      \section{Totals}
        \begin{center}
          \begin{tabular*}{0.75\textwidth}{@{\extracolsep{\fill}} | l | c || r | r | }
            \hline
            label 1 & label 2 & label 3 & label a \\ 
            \hline
            label 4 & label 5 & label 6 & label b \\ 
            \hline
            label 7 & label 8 & label 9 & label c \\
            \hline
          \end{tabular*}
        \end{center}
      \section{Month}
      \section{Day of Week}
        % standard suite of record lists for each
    \chapter{Time Span Records}
    % can span match types
      \section{Single Month}
      \section{Single Week}
      \section{Single Day}
    \chapter{Match Span Records}
      % single match type only
      \section{25 Matches}
      \section{20 Matches}
      \section{15 Matches}
      \section{10 Matches}
      \section{5 Matches}
      \section{3 Matches}
      \section{2 Matches}
    \chapter{Match Streak Records}
    \chapter{Single Match Records}
    \chapter{The Locations}
      \section{Superlatives}
      % match totals by location. match strength by location. lines by location. match type breakdown by location. time played by location. lps by location
      \section{23C}
      \section{11H}
      \section{1217 Edinburgh}
      \section{425 Arrow Rte}
      \section{207E Burbank} 
      \section{14211 Dickens}
      \section{Mt. Johnson}
    \chapter{The Players}
      \section{J.D.}
      \section{Dan}
      \section{Tom}
      \section{Jeran}
      \section{Ben}
      \section{Cameos}
    \chapter{Match Strength}
      % group streaks? -consec 3p matches with combined S ratio, 400 combined lines, consec matches without an individual S
    \chapter{Oddities}
  \appendix
  \part{Complete Match Transcript}
  \part{2004 Gaming Journal Excerpts}
  \part{Coding Journal Excerpts}
  \part{Web Resources}
  \clearpage
  \addcontentsline{toc}{part}{Index}
  \printindex
\end{document}
nothing typeset below the end tag